---
title: "hairsalon"
author: "A.Amstutz"
date: "2023-10-09"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: hide
  pdf_document:
    toc: yes
---

# Load packages
```{r load packages, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
```

# Sample Size calculation, according to "Calculation of sample size for a single cross-sectional cluster survey"
1) target population: All young women (= potential clients) in Lesotho.
2) estimated proportion of the outcome: We hypothesize that at least 77% of participants are comfortable with being offered one of the HIV/SRH services based on Bassett et al, J Acquir Immune Defic Syndr 2018, whereby 77% of clients were comfortable receiving PrEP at a hair salon.
any SRH service at the hair salon. Remember, in , it was over 90%.
3) 95% confidence interval: The probability that our sample results will be within the margin of error of the true population estimate. I.e, if we were to repeat our survey 100 times, we would get the same mean result about 95 times.
4) margin of error (precision): The maximum acceptable difference between our sample estimate and the true population parameter, i.e., how sure we need to be that the results are accurate for the entire population. Usually at around 5% or less. If we discover that 85% of our participating clients find the offer of any SRH service acceptable, we can safely assume that 80-90% of our clients will accept it.
5) intracluster correlation coefficient (ICC): The ICC measures the similarity or correlation between responses within the same cluster. Between 0-1. A higher ICC (closer to 1) implies more similarity (i.e. more correlation). Based on the ICC, the design effect, or inflation factor, is calculated. We assume an ICC of 0.05, probably lowest possible ICC for a behavioural outcome.
Based on: https://mnsurvey.nutritionintl.org/categories/13
6) If the ICC will be lower or we can recruit more cluster but with less participants (i.e., smaller cluster size) or we reach a higher acceptability -> power gain

```{r}
# Parameters for the sample size calculation
confidence_level <- 0.95 # confidence level
z <- qnorm(1 - (1 - confidence_level) / 2) # z statistic
d <- 0.05 # margin of error
cluster_size <- 3 # Average cluster size (fixed in our case)
icc <- 0.05
prop <- 0.77 # Estimated proportion (= 77% acceptability)
deff <- 1 + (cluster_size - 1) * icc # Design Effect
sample_size <- ceiling((z^2 * prop * (1 - prop) * deff) / d^2)
# Print the calculated sample size
cat("Required sample size:", sample_size)
# Number of clusters
n_clusters <- sample_size / cluster_size
cat("Required clusters:", round(n_clusters, 0))

# Create.a plot varying the ICC
icc_values <- seq(0.01, 0.09, by = 0.01)  # range of realistic ICCs
data_frame <- data.frame(ICC = icc_values)
# Calculate required sample size for each ICC value
data_frame$SampleSize <- ceiling((z^2 * prop * (1 - prop) * (1 + (cluster_size - 1) * data_frame$ICC)) / d^2)
# Create the plot
ss_plot <- ggplot(data_frame, aes(x = ICC, y = SampleSize)) +
  geom_line() +
  labs(
    x = "ICC (Intracluster Correlation Coefficient)",
    y = "Sample Size"
  ) +
  theme_minimal()
print(ss_plot)
# Save the ggplot as an image file (e.g., PNG)
ggsave("sample_size_plot.png", plot = ss_plot, width = 6, height = 4, units = "in")

# Print the current version of R
cat("R version:", R.version$version.string)

```

# Sample Size calculation, according to "Guidelines for Designing and Evaluating Feasibility Pilot Studies" https://pmc.ncbi.nlm.nih.gov/articles/PMC8849521/
1) The aim of the sample size calculation is to calculate the CI around the single proportion of PrEP uptake within 6 months in our pilot, to inform the larger cluster randomized trial
2) We take into account the clustering of the data, i.e., clusters = stylists with several clients.
3) Target population: Young women attending a hair salon in Lesotho, sexually active, HIV-
4) Estimated outcome: Based on the data from our citizen scientist survey, we estimate that 22% are taking up PrEP when offered
5) Determine the level of confidence: 95% confidence. The probability that our sample results will be within the margin of error of the true population estimate.
6) Determine the margin of error (precision): 10%. The maximum acceptable difference between our sample estimate and the true population parameter. If we find that 22% of our participating clients take up PrEP, we can safely assume that 12-32% of our target population will do so.
7) Estimate the intracluster correlation coefficient (ICC): The ICC measures the similarity or correlation between responses within the same cluster. Between 0-1. A higher ICC (closer to 1) implies more similarity (i.e. more correlation). Based on the ICC, the design effect, or inflation factor, is calculated. We calculated the ICC from our citizen scientist survey data.
8) Due to operational/budget reasons: max. 8 clusters

```{r}
# Parameters for the sample size calculation
confidence_level <- 0.95 # confidence level
z <- qnorm(1 - (1 - confidence_level) / 2) # z statistic
d <- 0.10 # margin of error
cluster_size <- 40 # Average cluster size (fixed in our case)
icc <- 0.10 # Intracluster correlation coefficient -> from the survey
prop <- 0.22 # Estimated proportion (= 22% demand), see above
deff <- 1 + (cluster_size - 1) * icc # Design Effect
sample_size <- ceiling((z^2 * prop * (1 - prop) * deff) / d^2)
# Print the calculated sample size
cat("Required sample size:", sample_size)
# Number of clusters
n_clusters <- sample_size / cluster_size
cat("Required clusters:", round(n_clusters, 0))

# Create.a plot varying the ICC
icc_values <- seq(0.01, 0.20, by = 0.03)  # range of realistic ICCs
data_frame <- data.frame(ICC = icc_values)
# Calculate required sample size for each ICC value
data_frame$SampleSize <- ceiling((z^2 * prop * (1 - prop) * (1 + (cluster_size - 1) * data_frame$ICC)) / d^2)
# Create the plot
ss_plot <- ggplot(data_frame, aes(x = ICC, y = SampleSize)) +
  geom_line() +
  labs(
    x = "ICC (Intracluster Correlation Coefficient)",
    y = "Sample Size"
  ) +
  theme_minimal()
print(ss_plot)

# Save the ggplot as an image file (e.g., PNG)
ggsave("sample_size_plot.png", plot = ss_plot, width = 6, height = 4, units = "in")

# Print the current version of R
cat("R version:", R.version$version.string)

```
